Paper Figures and Text

### 2024-04-22 Fish Data Analysis/Paper_Figures.qmd
Text changes

text_size = 16

@@

perp_angle_lm_close <- lm(Fish1_Yaw_Heading_PS ~ Ablation*Darkness, data = perp_angle_df %>% filter(Dist_Cat == "Close"))
Anova(perp_angle_lm_close)
emmeans(perp_angle_lm_close, specs = pairwise ~ Ablation:Darkness)

my_comparisons <- list(c("No Ablation, Light", "Ablated, Dark"),
                       c("No Ablation, Dark", "Ablated, Dark"))

heading_PS_graph_close <- ggplot(perp_angle_df %>% filter(Dist_Cat == "Close"),
                                 aes(x = interaction(Ablation, Darkness, sep =", "), y = rad2deg(Fish1_Yaw_Heading_PS),
                          fill = interaction(Ablation, Darkness, sep =", "), color = interaction(Ablation, Darkness, sep =", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth*0.375, "npc")) +
  geom_point(aes(y = rad2deg(mean_turn)), size = 5, color = "black") +
  geom_line(aes(y = rad2deg(mean_turn), group = 1), size = 1, color = "black") +
  geom_errorbar(aes(ymin=rad2deg(mean_turn-sd_turn), ymax=rad2deg(mean_turn+sd_turn)), width=.2, color = "black")+
  theme_light()+
  scale_fill_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  scale_color_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  theme(legend.position = "none")+
  xlab("")+
  ylab("Focal Fish Turning Angular Speed (Degrees / s)")+
  scale_y_continuous(breaks = seq(-180,180, 60))+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

perp_angle_lm_far <- lm(Fish1_Yaw_Heading_PS ~ Ablation*Darkness, data = perp_angle_df %>% filter(Dist_Cat == "Far"))
Anova(perp_angle_lm_far)
emmeans(perp_angle_lm_far, specs = pairwise ~ Ablation:Darkness)

@@

heading_PS_graph_far <- ggplot(perp_angle_df %>% filter(Dist_Cat == "Far"),
                                 aes(x = interaction(Ablation, Darkness, sep =", "), y = rad2deg(Fish1_Yaw_Heading_PS),
                          fill = interaction(Ablation, Darkness, sep =", "), color = interaction(Ablation, Darkness, sep =", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth*0.375, "npc")) +
  geom_point(aes(y = rad2deg(mean_turn)), size = 5, color = "black") +
   geom_line(aes(y = rad2deg(mean_turn), group = 1), size = 1, color = "black") +
  geom_errorbar(aes(ymin=rad2deg(mean_turn-sd_turn), ymax=rad2deg(mean_turn+sd_turn)), width=.2, color = "black")+
  theme_light()+
  scale_fill_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  scale_color_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  theme(legend.position = "none")+
  xlab("")+
  ylab("Focal Fish Turning Angular Speed (Degrees / s)")+
  scale_y_continuous(breaks = seq(-180,180, 60))+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

@@

ggsave("Paper Figures/heading_PS_mega_plot.png", heading_PS_mega_plot, width = 14, height = 7)

@@

my_comparisons <- list(c("No Ablation, Light", "No Ablation, Dark"),
                       c("No Ablation, Light", "Ablated, Dark"),
                       c("Ablated, Light", "No Ablation, Dark"),
                       c("Ablated, Light", "Ablated, Dark"))

nnd_still <- ggplot(school_data %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = NND,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = NND_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=NND_Mean_Val-NND_SD_Val, ymax=NND_Mean_Val+NND_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Still Water") +
  xlab("") +
  ylab("School NND (BL)") +
  theme_light()+ 
  theme(legend.position = "none") +
  #ylim(0,2.5)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

my_comparisons <- list(c("Ablated, Light", "No Ablation, Dark"))

nnd_flow <- ggplot(school_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = NND,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = NND_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=NND_Mean_Val-NND_SD_Val, ymax=NND_Mean_Val+NND_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Flow (2 BL/s)") +
  xlab("") +
  ylab("School NND (BL)") +
  theme_light()+ 
  theme(legend.position = "none") +
  #ylim(0,5)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

nnd_still
nnd_flow

nnd_glm <- glm(NND ~ Ablation*Darkness*Flow, data = school_data)
Anova(nnd_glm)
emmeans(nnd_glm, specs = pairwise ~ Ablation:Darkness | Flow)

@@

my_comparisons <- list()

polar_still <- ggplot(school_data %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = School_Polar,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = Polar_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Polar_Mean_Val-Polar_SD_Val, ymax=Polar_Mean_Val+Polar_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  #ggtitle("Effect of Available Senses on Polarization in Still Water") +
  xlab("") +
  ylab("Polarization") +
  theme_light()+ 
  theme(legend.position = "none") +
  ylim(0,1)+
  scale_y_continuous(breaks = c(0,0.25,0.5,0.75,1))+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

my_comparisons <- list()

polar_flow <- ggplot(school_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = School_Polar,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = Polar_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Polar_Mean_Val-Polar_SD_Val, ymax=Polar_Mean_Val+Polar_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  #ggtitle("Effect of Available Senses on Polarization in Flowing Water (2 BL/s)") +
  xlab("") +
  ylab("Polarization") +
  theme_light()+ 
  theme(legend.position = "none") +
  ylim(0,1)+
  scale_y_continuous(breaks = c(0,0.25,0.5,0.75,1))+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

polar_still
polar_flow

polar_glm <- glm(School_Polar ~ Ablation*Darkness*Flow, data = school_data)
Anova(polar_glm)
emmeans(polar_glm, specs = pairwise ~ Ablation:Darkness | Flow)
```

@@

```{r}
my_comparisons <- list()

speed_still <- ggplot(school_data %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = School_Speed,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = Speed_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=max(Speed_Mean_Val-Speed_SD_Val,0), ymax=Speed_Mean_Val+Speed_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  #ggtitle("Effect of Available Senses on Speed (BL/s) in Still Water") +
  xlab("") +
  ylab("Mean Speed of Fish (BL/s)") +
  theme_light()+ 
  theme(legend.position = "none") +
  ylim(0,6)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

my_comparisons <- list()

speed_flow <- ggplot(school_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = School_Speed,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = Speed_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Speed_Mean_Val-Speed_SD_Val, ymax=Speed_Mean_Val+Speed_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  #ggtitle("Effect of Available Senses on Speed (BL/s) in Flowing Water (2 BL/s)") +
  xlab("") +
  ylab("Mean Speed of Fish (BL/s)") +
  theme_light()+ 
  theme(legend.position = "none") +
  ylim(0,6)+
  stat_compare_means(comparisons = my_comparisons, label.y = c(5.5), label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

speed_still
speed_flow

speed_glm <- glm(School_Speed ~ Ablation*Darkness*Flow, data = school_data)
Anova(speed_glm)
emmeans(speed_glm, specs = pairwise ~ Ablation:Darkness | Flow)
```

@@

group_still <- ggplot(group_sum_data %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "),
           y = count,
           fill = Groups)) + 
    geom_bar(position="fill", stat="identity")+
    xlab("") +
    ylab("Proportion of Time") +
    theme_light()+ 
    scale_fill_manual(values=c("8" = "#1D3557","7" = "#325A7C","6" = "#457B9D","5" = "#7BAFBF",
                               "4" = "#A8DADC","3" = "#D0EBE6","2" = "#F1FAEE","1" = "#3ae639")) +
    theme(axis.text.x = element_text(size = text_size),
          axis.text.y = element_text(size = text_size),
          axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

group_flow <- ggplot(group_sum_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = interaction(Ablation,Darkness,sep=", "),
           y = count,
           fill = Groups)) + 
    geom_bar(position="fill", stat="identity")+
    xlab("") +
    ylab("Proportion of Time") +
    theme_light()+ 
    scale_fill_manual(values=c("8" = "#1D3557","7" = "#325A7C","6" = "#457B9D","5" = "#7BAFBF",
                               "4" = "#A8DADC","3" = "#D0EBE6","2" = "#F1FAEE","1" = "#3ae639")) +
    theme(axis.text.x = element_text(size = text_size),
          axis.text.y = element_text(size = text_size),
          axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

group_still
group_flow

groups_glm <- glm(Groups ~ Ablation*Darkness*Flow, data = school_data, family  = poisson)
Anova(groups_glm)
emmeans(groups_glm, specs = pairwise ~ Ablation:Darkness | Flow)

groups_glm_still <- glm(Groups ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Still Water"), family  = poisson)
Anova(groups_glm_still, test.statistic="F")

groups_glm_flow <- glm(Groups ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"), family  = poisson)
Anova(groups_glm_flow, test.statistic="F")

@@

ggsave("Paper Figures/school_stats_mega_plot.png", school_stats_mega_plot, width = 12, height = 17)
```

>>>>

text_size = 16
sig_text_size = 6

@@

sig_dict <- list("No Ablation, Light" = "A", "Ablated, Light" = "B","No Ablation, Dark" = "A", "Ablated, Dark" = "B")
perp_angle_df$sig_letters <- unlist(sig_dict[interaction(perp_angle_df$Ablation, perp_angle_df$Darkness, sep =", ")])

heading_PS_graph_close <- ggplot(perp_angle_df %>% filter(Dist_Cat == "Close"),
                                 aes(x = interaction(Ablation, Darkness, sep =", "), y = rad2deg(Fish1_Yaw_Heading_PS),
                          fill = interaction(Ablation, Darkness, sep =", "), color = interaction(Ablation, Darkness, sep =", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth*0.375, "npc")) +
  geom_point(aes(y = rad2deg(mean_turn)), size = 5, color = "black") +
  geom_line(aes(y = rad2deg(mean_turn), group = 1), size = 1, color = "black") +
  geom_errorbar(aes(ymin=rad2deg(mean_turn-sd_turn), ymax=rad2deg(mean_turn+sd_turn)), width=.2, color = "black")+
  theme_light()+
  scale_fill_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  scale_color_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  theme(legend.position = "none")+
  xlab("")+
  ylab("Focal Fish Turning Angular Speed (Degrees / s)")+
  scale_y_continuous(breaks = seq(-180,180, 60), limits = c(-180,300))+
  geom_text(aes(label = sig_letters, y = 300), color = "black", size = sig_text_size) +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

@@

sig_dict <- list("No Ablation, Light" = "A", "Ablated, Light" = "A","No Ablation, Dark" = "B", "Ablated, Dark" = "B")
perp_angle_df$sig_letters <- unlist(sig_dict[interaction(perp_angle_df$Ablation, perp_angle_df$Darkness, sep =", ")])

heading_PS_graph_far <- ggplot(perp_angle_df %>% filter(Dist_Cat == "Far"),
                                 aes(x = interaction(Ablation, Darkness, sep =", "), y = rad2deg(Fish1_Yaw_Heading_PS),
                          fill = interaction(Ablation, Darkness, sep =", "), color = interaction(Ablation, Darkness, sep =", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth*0.375, "npc")) +
  geom_point(aes(y = rad2deg(mean_turn)), size = 5, color = "black") +
   geom_line(aes(y = rad2deg(mean_turn), group = 1), size = 1, color = "black") +
  geom_errorbar(aes(ymin=rad2deg(mean_turn-sd_turn), ymax=rad2deg(mean_turn+sd_turn)), width=.2, color = "black")+
  geom_text(aes(label = sig_letters, y = 300), color = "black", size = sig_text_size) +
  theme_light()+
  scale_fill_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  scale_color_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  theme(legend.position = "none")+
  xlab("")+
  ylab("Focal Fish Turning Angular Speed (Degrees / s)")+
  scale_y_continuous(breaks = seq(-180,180, 60), limits = c(-180,300))+
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

@@

ggsave("Paper Figures/Figure 3.png", heading_PS_mega_plot, width = 14, height = 7)

@@

sig_dict <- list("No Ablation, Light" = "A", "Ablated, Light" = "A","No Ablation, Dark" = "B", "Ablated, Dark" = "B")
school_data$sig_letters <- unlist(sig_dict[interaction(school_data$Ablation, school_data$Darkness, sep =", ")])

nnd_still <- ggplot(school_data %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = NND,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = NND_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=NND_Mean_Val-NND_SD_Val, ymax=NND_Mean_Val+NND_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Still Water") +
  xlab("") +
  ylab("School NND (BL)") +
  theme_light()+ 
  theme(legend.position = "none") +
  #ylim(0,2.5)+
  geom_text(aes(label = sig_letters, y = 4), color = "black", size = sig_text_size) +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

sig_dict <- list("No Ablation, Light" = "", "Ablated, Light" = "","No Ablation, Dark" = "", "Ablated, Dark" = "")
school_data$sig_letters <- unlist(sig_dict[interaction(school_data$Ablation, school_data$Darkness, sep =", ")])

nnd_flow <- ggplot(school_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = NND,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = NND_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=NND_Mean_Val-NND_SD_Val, ymax=NND_Mean_Val+NND_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Flow (2 BL/s)") +
  xlab("") +
  ylab("School NND (BL)") +
  theme_light()+ 
  theme(legend.position = "none") +
  #ylim(0,5)+
  geom_text(aes(label = sig_letters, y = 4), color = "black", size = sig_text_size) +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

nnd_still
nnd_flow
```

@@

sig_dict <- list("No Ablation, Light" = "", "Ablated, Light" = "","No Ablation, Dark" = "", "Ablated, Dark" = "")
school_data$sig_letters <- unlist(sig_dict[interaction(school_data$Ablation, school_data$Darkness, sep =", ")])

polar_still <- ggplot(school_data %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = School_Polar,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = Polar_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Polar_Mean_Val-Polar_SD_Val, ymax=Polar_Mean_Val+Polar_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  #ggtitle("Effect of Available Senses on Polarization in Still Water") +
  xlab("") +
  ylab("Polarization") +
  theme_light()+ 
  theme(legend.position = "none") +
  ylim(0,1)+
  scale_y_continuous(breaks = c(0,0.25,0.5,0.75,1))+
  geom_text(aes(label = sig_letters, y = 1.1), color = "black", size = sig_text_size) +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

sig_dict <- list("No Ablation, Light" = "A", "Ablated, Light" = "A","No Ablation, Dark" = "A", "Ablated, Dark" = "B")
school_data$sig_letters <- unlist(sig_dict[interaction(school_data$Ablation, school_data$Darkness, sep =", ")])

polar_flow <- ggplot(school_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = School_Polar,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = Polar_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Polar_Mean_Val-Polar_SD_Val, ymax=Polar_Mean_Val+Polar_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  #ggtitle("Effect of Available Senses on Polarization in Flowing Water (2 BL/s)") +
  xlab("") +
  ylab("Polarization") +
  theme_light()+ 
  theme(legend.position = "none") +
  ylim(0,1)+
  scale_y_continuous(breaks = c(0,0.25,0.5,0.75,1))+
  geom_text(aes(label = sig_letters, y = 1.1), color = "black", size = sig_text_size) +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

polar_still
polar_flow
```

@@

```{r}
sig_dict <- list("No Ablation, Light" = "", "Ablated, Light" = "","No Ablation, Dark" = "", "Ablated, Dark" = "")
school_data$sig_letters <- unlist(sig_dict[interaction(school_data$Ablation, school_data$Darkness, sep =", ")])

speed_still <- ggplot(school_data %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = School_Speed,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = Speed_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=max(Speed_Mean_Val-Speed_SD_Val,0), ymax=Speed_Mean_Val+Speed_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  #ggtitle("Effect of Available Senses on Speed (BL/s) in Still Water") +
  xlab("") +
  ylab("Mean Speed of Fish (BL/s)") +
  theme_light()+ 
  theme(legend.position = "none") +
  ylim(0,6)+
  geom_text(aes(label = sig_letters, y = 5.5), color = "black", size = sig_text_size) +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

sig_dict <- list("No Ablation, Light" = "", "Ablated, Light" = "","No Ablation, Dark" = "", "Ablated, Dark" = "")
school_data$sig_letters <- unlist(sig_dict[interaction(school_data$Ablation, school_data$Darkness, sep =", ")])

speed_flow <- ggplot(school_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = School_Speed,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = Speed_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Speed_Mean_Val-Speed_SD_Val, ymax=Speed_Mean_Val+Speed_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  #ggtitle("Effect of Available Senses on Speed (BL/s) in Flowing Water (2 BL/s)") +
  xlab("") +
  ylab("Mean Speed of Fish (BL/s)") +
  theme_light()+ 
  theme(legend.position = "none") +
  ylim(0,6)+
  geom_text(aes(label = sig_letters, y = 5.5), color = "black", size = sig_text_size) +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

speed_still
speed_flow
```

@@

sig_dict <- list("No Ablation, Light" = "A", "Ablated, Light" = "A","No Ablation, Dark" = "B", "Ablated, Dark" = "B")
group_sum_data$sig_letters <- unlist(sig_dict[interaction(group_sum_data$Ablation, group_sum_data$Darkness, sep =", ")])

group_still <- ggplot(group_sum_data %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "),
           y = count,
           fill = Groups)) + 
    geom_bar(position="fill", stat="identity")+
    xlab("") +
    ylab("Proportion of Time") +
    theme_light()+ 
    scale_fill_manual(values=c("8" = "#1D3557","7" = "#325A7C","6" = "#457B9D","5" = "#7BAFBF",
                               "4" = "#A8DADC","3" = "#D0EBE6","2" = "#F1FAEE","1" = "#3ae639")) +
    geom_text(aes(label = sig_letters, y = 1.1), color = "black", size = sig_text_size) +
    theme(axis.text.x = element_text(size = text_size),
          axis.text.y = element_text(size = text_size),
          axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

sig_dict <- list("No Ablation, Light" = "", "Ablated, Light" = "","No Ablation, Dark" = "", "Ablated, Dark" = "")
group_sum_data$sig_letters <- unlist(sig_dict[interaction(group_sum_data$Ablation, group_sum_data$Darkness, sep =", ")])

group_flow <- ggplot(group_sum_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = interaction(Ablation,Darkness,sep=", "),
           y = count,
           fill = Groups)) + 
    geom_bar(position="fill", stat="identity")+
    xlab("") +
    ylab("Proportion of Time") +
    theme_light()+ 
    scale_fill_manual(values=c("8" = "#1D3557","7" = "#325A7C","6" = "#457B9D","5" = "#7BAFBF",
                               "4" = "#A8DADC","3" = "#D0EBE6","2" = "#F1FAEE","1" = "#3ae639")) +
    geom_text(aes(label = sig_letters, y = 1.1), color = "black", size = sig_text_size) +
    theme(axis.text.x = element_text(size = text_size),
          axis.text.y = element_text(size = text_size),
          axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

group_still
group_flow
```

@@

ggsave("Paper Figures/Figure 2.png", school_stats_mega_plot, width = 12, height = 17)
```
